---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# projectr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/djnavarro/projectr.svg?branch=master)](https://travis-ci.org/djnavarro/projectr)
<!-- badges: end -->

The goal of projectr is to let me manage my projects within R. It's very minimal in design, and does not track hours spent. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("djnavarro/projectr")
```
## Example 1

```{r example}
library(projectr)

# set the folder to store data (normally you'd specify this in
# the .Rprofile to ensure it's always available)
projectr_home(path = tempdir())

# initially we have no jobs
view_joblist()

# initially we know no people
people_list()

# add some people
people_add(name = "Bora Horza Gobuchul", nickname = "horza")
people_add(name = "Perosteck Balveda", nickname = "balveda")
people_list()

# add a job with the required options only
job_create(name = "findmind", 
           description = "Find the refugee Culture Mind", 
           owner = "horza")

job_create(name = "getback", 
           description = "Return to Schaar to find her", 
           owner = "horza")

# now take a look
view_joblist()

# you can look at a specific job:
view_job("findmind")
```

## Example 2

Jobs can be specified in more detail

```{r example2}
job_create(name = "findhorza", 
           description = "Find Horza", 
           owner = "balveda",
           status = "active",
           priority = 1,
           deadline = NA,
           path = "~/myprojects/findhorza",
           urls = list(
             github = "https://github.com/balveda/notarealthing",
             overleaf = "https://overleaf.com/dklgjslkfjaslkfj")
           )

# now take a look
view_joblist()

# filter the job list (currently doesn't support nicknames)
view_joblist(owner == "Bora Horza Gobuchul")
```

Everything is stored in plain text files. There is a JSON file containing the jobs, and a CSV file containing the table of names. To avoid the tediousness of calling `projectr_home` every session you can include a line like this in .Rprofile

```
options(projectr.home = "~/GitHub/utilities/projects/")
```

A "job" is stored as a list that contains the following fields

- `name`: name of the project to create
- `description`: brief description of the project
- `owner`: should be a name or a nickname
- `status`: should be "active", "inactive", "complete", "abandoned"
- `team`: should be a vector of names/nicknames (owner is automatically included)
- `priority`: numeric
- `deadline`: a date
- `path`: path to the project home directory
- `urls`: list of urls
- `tasks`: list of tasks
- `notes`: list of notes

The intention is to allow jobs to include a set of "tasks" which are structured objects in their own right, and to allow jobs and tasks to be filtered by the due date of tasks (e.g., you should be able to pull out of a list of tasks due before a specific date). The functionality for "notes" hasn't been determined yet, but the intention is *not* to turn this into a project log or anything like that. Each project should maintain its own logs, readmes, etc: that is deliberately outside the scope of projectr!

Functions are organised as:

- `job_*` functions create, delete and edit job
- `view_*` functions display information about jobs
- `goto_*` functions navigate to projects/url

There are a few functions that don't currently fit this scheme. WIP.

