---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# projectr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/djnavarro/projectr.svg?branch=master)](https://travis-ci.org/djnavarro/projectr)
[![CRAN status](https://www.r-pkg.org/badges/version/projectr)](https://cran.r-project.org/package=projectr)
<!-- badges: end -->

The goal of projectr is to provide tools for project management within R. The 
design is very minimal at the moment. It allows the user to store and edit 
basic metadata associated with projects. It allows you to search, filter and 
navigate between projects. Prioritisation and deadlines are supported, but 
financial information and time spent on a project are not tracked. 


## Installation

The projectr package has not been released on CRAN. However you can install the
development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("djnavarro/projectr")
```

The package is built around three families of functions:

- the `job_*` functions create, delete and edit a job
- the `view_*` functions display information about jobs
- the `goto_*` functions navigate to projects and webpages

(though there are a few functions that don't currently fit this scheme)

## Example 1: Getting started

The projectr package stores information about projects in a few files stored
within a directory referred to as the "projectr home". The easiest way to set
this location in a persistent way is to edit the .Rprofile file to include
the following line:

```{r, eval = FALSE}
options(projectr.home = "PATH_TO_PROJECT_FOLDER")
```
```{r, include=FALSE}
# for the purposes of the demo, set the projectr home to a temp directory 
projectr::projectr_home(path = tempdir())
```

This ensures that whenever the projectr package is loaded it knows where to find your project information. Once this is done, you can start adding *jobs*. A "job" is intended to be much the same as a "project", but to avoid confusion with "RStudio projects" a different term is used. Here's how to add and view the jobs you have stored:

```{r createprojects}
library(projectr)

view_joblist()

job_create(
  name = "workitout", 
  description = "sip martinis and party in France", 
  owner = "britney"
)

view_joblist()
```

Projects can be deleted by name:

```{r deleteprojects}
job_delete("workitout")
view_joblist()
```

## Example 2: People, owners and teams

The projectr package stores a data base of names and nicknames, so you can specify a person using their nickname instead of needing to type the full name:

```{r managepeople}
people_add("Beyoncé Knowles", "beyonce")
people_add("Kelly Rowland", "kelly")
people_add("Michelle Williams", "michelle")
people_list()
```

Jobs can consist of multiple people on a *team* but the job must have a single *owner*, a named team member who is responsible for the project. When used in conjunction with nicknames, the `job_create()` function allows you to specify the team efficiently:

```{r addbynickmame}
job_create(
  name = "survivor",
  description = "Run a survival analysis",
  owner = "beyonce",
  team = c("kelly", "michelle"),
  priority = 1,
  status = "inactive"
)
```

The owner of a job will automatically be added to the team. As before we can use `view_joblist()` to provide a summary of all listed jobs, which in this case is only a single job, but you can also use `view_job()` to look at a single job in more detail:

```{r viewjob}
view_joblist()


view_job("survivor")
```


## Example 3: Editing jobs

Internally, a "job" is represented as a list with the following fields

- `name`: name of the project
- `description`: brief description of the project
- `owner`: should be a name or a nickname
- `status`: should be "active", "inactive", "complete", "abandoned"
- `team`: should be a vector of names/nicknames (owner is automatically included)
- `priority`: numeric
- `deadline`: a date
- `path`: path to the project home directory
- `urls`: list of urls
- `tasks`: list of tasks (currently doesn't work)
- `notes`: list of notes (currently doesn't work)

When we added the "survival" job earlier, we specified some of these fields but not others. There are three functions that you can use to modify the properties of a job:

- `job_edit()` can reset the value of any field
- `job_edit_team()` makes it easier to edit the team
- `job_edit_urls()` makes it easier to edit the list of webpages associated with a job

To be continued...
