---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# workbch

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/djnavarro/workbch.svg?branch=master)](https://travis-ci.org/djnavarro/workbch)
[![CRAN status](https://www.r-pkg.org/badges/version/workbch)](https://cran.r-project.org/package=workbch)
[![Codecov test coverage](https://codecov.io/gh/djnavarro/workbch/branch/master/graph/badge.svg)](https://codecov.io/gh/djnavarro/workbch?branch=master)
<!-- badges: end -->

The workbch package provides a "work bench" of tools for project management  within R, based around the concept of a "job" (which might map to a single RStudio project or a single git repository). Jobs can be linked to multiple URLs, etc. In addition to basic tracking, searching and filtering, the package provides some tools to navigate between jobs, browse relevant websites, and check the git status of repositories linked to a job. 

## Installation

The workbch package has not been released on CRAN. You can install the
development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("djnavarro/workbch")
```

The package is built from four families of functions:

- the `make_*` functions make jobs
- the `set_*` functions edit jobs
- the `view_*` functions display information about jobs
- the `goto_*` functions navigate to projects and webpages
- the `delete_*` functions delete jobs, tasks, etc

## Example 1: Getting started

The workbch package stores information in a few files that are stored
within a directory referred to as the "workbch home". The easiest way to set
this location in a persistent way is to edit the .Rprofile file to include
the following line:

```{r, eval = FALSE}
options(workbch.home = "PATH_TO_FOLDER")
```
```{r, include=FALSE}
# for the purposes of the demo, set the workbch home to a temp directory 
workbch::workbch_sethome(path = tempdir())
```

This ensures that when the workbch package is loaded it knows where to find information about jobs. Once this is done, you can start adding jobs! A "job" is intended to have roughly the same meaning as a "project" in everyday life (i.e., a self-contained body of work of some kind), but to avoid confusion with "RStudio projects" I've used a different term. Here's how to add and view the jobs you have stored:

```{r makejobs}
library(workbch)

view_jobs()

make_job(
  jobname = "workitout", 
  description = "Sip martinis and party in France", 
  owner = "Britney Spears"
)

view_jobs()
```

Jobs can be deleted by name:

```{r deletejobs}
delete_job("workitout")
view_jobs()
```


## Example 3: Editing jobs

To illustrate, suppose we make a new job, called "toxic":

```{r maketoxic}
make_job(
  jobname = "toxic",
  description = "Estimate the LD50 dose",
  owner = "Britney Spears",
  priority = 2,
  status = "active",
  path = "~/projects/toxic"
)
view_job("toxic")
```

If at this point we realise the priority should have been set at 1, or we want to add some URLS:

```{r editteam}
workbch_setjob(jobname = "toxic", priority = 1)
workbch_setjob(jobname = "toxic", site = "github", link = "https://github.com/djnavarro/toxic")
workbch_setjob(jobname = "toxic", site = "genius", link = "https://genius.com/Britney-spears-toxic-lyrics")
view_job("toxic")
```

If `jobname` argument is not specified, the workbch package attempts to see if the use is working within a known job. It checks for this in two ways. If the current RStudio project matches a known job, then that job is used by default. Failing that, the working directory is checked.

## Example 4: Filtering and prioritising

After a while one can easily end up with a lot of jobs, and it can be hard to find what you're looking for (or, if you're like me, get anxious at seeing so many things that you have to do). For example:

```{r include=FALSE}
make_job("hitmebaby", "Signal detection modelling", "Britney Spears", priority = 2)
make_job("spinspinsugar", "Check for periodicities", "Sneakerpimps", priority = 1)
make_job("boys", "Distributional assumptions", "Lizzo", priority = 2)
```
```{r busystate}
view_jobs()
```

A simple way to only see the high priority jobs:

```{r prioritise}
view_priorities()
```

More generally, `view_jobs()` and `view_priorities()` both allow you to pass filtering expressions to `dplyr::filter()` to extract the subset you're interested in. Suppose I only want to see the high priority active jobs:

```{r filtering}
view_jobs(priority == 1 & status == "active")
```

Indeed `view_priorities()` function is essentially a helper function to avoid having to type `view_jobs(priority == 1)` on a regular basis. 

## Example 5: Navigation

To open a webpage associated with a job, it is as simple as using the `goto_url()` function:

```{r eval=FALSE}
goto_url("toxic", "github")
```

To open the corresponding RStudio project (assuming that there is an RStudio project file located in the directory specified as the project path)...

```{r eval=FALSE}
goto_project("toxic")
```

If there is no RStudio project at the relevant location, or the RStudio API is not available (i.e., RStudio is not running), all this function will do is use `setwd()` to change the working directory.

